Comparing Power Optimizations in the Reorder Buffer

### 2011-06-09 paper/end.tex
latch results

>>>>

\subsection{Omited Output Port ROB}
The Latch ROB results shown in the tables are produced from the parameters 
speficed above with 16 FIFO retention latches. Looking at the result tables,
 we see that the OOP ROB has comperable performance (in cycle) when compared 
to basline Circular ROB.  Showing that the additional slowdown caused by the
 non-availibilty of the operand when it enters the ROB is negligible, which
matches with the designers argument \cite{kucuk}.

Next we see that the rest of the power usage parameters are have all been 
increased.  Both the bit cycles and transitions to high are slightly higher.
This is to be expected since there is the additional retention latches 
strucure, which makes the ROB larger and thus more bits to have a transition
to the high state.  The same logic applies to the large increase of the
register comparators used.  Each check for an operand has to check the
register tag of all the elements in the ROB, and the rentention latches 
as well.

From the results tables, it appears that there is no reasonable reason to use
the OOP ROB.  This is untrue, as the the read port usages for the OOP drops
significantly.  Since we approximate about 6\% forwarding from the ROB, of 
100,000 instructions, we would need to foward about 6,000 operands (as a
lower bound, assuming all the instructions were INT ops).  This equates to
192,000, bit lines that needs to be driven for operand forwading.  Also with
the elimination of the forwarding ports, the design of the ROB becomes much 
simplier as well. With increasing forward rates required, the energy savings
will increase.
